### 2023-08-15 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
small changes

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Biological membranes, the basic structural units for compartmentalizing
biological systems, have been observed to contain a vast array of
proteins and different lipid species that phase-separate and form
domains or rafts, resulting in spatial variations in material properties
such as bending stiffness. Synthetic multicomponent vesicles,
self-enclosed lipid bilayer membranes composed of different lipid
species, have been used to study the rich patterns and accompanying
morphologies that emerge from elastic heterogeneity in the membrane. In
a quiescent environment, such elastic heterogeneity gives rise to
wrinkling budding~\cite{Lowengrub2009_PRE, Li2012_CommMathSci}, adhesion
and fusion~\cite{Zhao2011_PRE} of vesicle membrane, closely related to
cellular budding and fission processes~\cite{Rauch2000_BiophysJ} as well
as in cellular adhesion and fusion~\cite{Takeda2003_PNAS}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:NumericalMethods}Numerical Methods}
We use a high-order integral equation formulation to resolve the complex
vesicle shapes and long-range hydrodynamic interactions. The velocity
field $\uu$ at $\xx \in \Omega$ is written as a combination of a
single-layer potential and a double-layer potential
\begin{align}
  \label{eqn:LPrep}
  \uu(\xx) = S[\ff](\xx) + D[\eeta](\xx),
\end{align}
where
\begin{align}
  S[\ff](\xx) &= \frac{1}{4\pi\mu} \int_{\gamma} \left(
    -\log \rho \mathds{I} + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) \, ds_\yy, \\
%
    D[\eeta](\xx) &= \frac{1}{\pi} \int_{\Gamma} 
      \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} \eeta(\yy) \, ds_\yy,
\end{align}
$\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times 2$
identity matrix. The corresponding pressure is
\begin{align}
  p(\xx) = \frac{1}{2\pi} \int_{\gamma} \frac{\rr \cdot \ff}{\rho^2} \, ds_\yy + 
    \frac{1}{\pi} \int_{\Gamma} \frac{1}{\rho^2} 
    \left(\mathds{I} - 2\frac{\rr \otimes \rr}{\rho^2} \right) 
    \nn \cdot \eeta \, ds_\yy.
\end{align}

@@

We also report the excess pressure for the stenosis geometry and relate
it to the size of the lubrication layers. The excess pressure is the
additional pressure that is required to pass the vesicle through the
geometry when compared to the pressure necessary if the vesicle were
absent. Average pressures are calculated along cross-sections that are
parallel to the flow direction near the inlet and outlet of the
stenosis, and the vesicle itself is never near these locations.

@@

When a vesicle is tank-treading near a solid wall, the flow in the thin
layer of fluid includes both a linear profile and a Poiseuille
profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
The magnitude of the Poiseuille profile is determined by the pressure
gradient between the vesicle and the solid wall, while the linear
profile is determined by the tangential velocity of the vesicle relative
to the solid wall. Using the definition of the lubrication layer
outlined in Section~\ref{sec:LL}, we consider the flow profile inside
this lubrication layer in Figure~\ref{fig:BLvelocities}. We observe that
the Poiseuille coefficient can be either positive or negative, meaning
that the pressure in the lubrication layer switches signs. This behavior
is caused when the tangential force on the vesicle
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u},
\end{align}
is sufficiently large to offset the flow driven by the boundary
conditions defined at the inlet and outlet of the geometry. Here,
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the derivative of the membrane energy with respect to the lipid
concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential force is $\mathbf{F}_\tt =
-\sigma_s$ which is the usual Marangoni effect.

@@

We conclude this example by considering the different shapes and
energies that single-component and multicomponent shapes display. Since
we have initialized the lipid species to initially be phase separated,
the phase energy is nearly constant for all cases, and is therefore not
plotted. The tension energy, on the other hand, increases as the vesicle
approaches the neck, but its general shape is similar for all five
cases, and it too is not plotted. However, the bending energies show
different behaviors for each of the cases (Figure~\ref{fig:bendingAll}).
The main difference being that the multicomponent vesicles with a higher
percentage of floppy regions have less bending energy, especially as the
vesicle passes through the neck. We also note that the bending energy
undergoes several transient increases and decreases. These occur when
the tail of the vesicle undergoes transitions from lower energy shapes,
such as `C' or `S' shapes, to high energy shapes, such as `W' shapes.
Figure~\ref{fig:bendingSC_contracting} shows these different vesicle
shapes for the single-component vesicle and multicomponent vesicle that
is 45\% floppy. The shapes at several critical points along the bending
energy are included.
%and we can indeed see that transitioning vesicle shape between these
%different states.

>>>>

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Biological membranes, the basic structural units for compartmentalizing
biological systems, have been observed to contain a vast array of
proteins and different lipid species that phase-separate and form
domains or rafts, resulting in spatial variations in material properties
such as bending stiffness. Synthetic multicomponent vesicles,
self-enclosed lipid bilayer membranes composed of different lipid
species, have been used to study the rich patterns and accompanying
morphologies that emerge from elastic heterogeneity in the membrane. In
a quiescent environment, such elastic heterogeneity gives rise to
wrinkling, budding, adhesion, and fusion of vesicle
membranes~\cite{Lowengrub2009_PRE, Li2012_CommMathSci, Zhao2011_PRE},
closely related to several cellular processes~\cite{Rauch2000_BiophysJ,
Takeda2003_PNAS}.
%In a quiescent environment, such elastic heterogeneity gives rise to
%wrinkling budding~\cite{Lowengrub2009_PRE, Li2012_CommMathSci},
%adhesion and fusion~\cite{Zhao2011_PRE} of vesicle membrane, closely
%related to cellular budding and fission
%processes~\cite{Rauch2000_BiophysJ} as well as in cellular adhesion and
%fusion~\cite{Takeda2003_PNAS}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:NumericalMethods}Numerical Methods}
We use a high-order integral equation formulation to resolve the complex
vesicle shapes and long-range hydrodynamic interactions. The velocity
field $\uu$ at $\xx \in \Omega$ is written as a combination of a
single-layer potential and a double-layer potential
\begin{align}
  \label{eqn:LPrep}
  \uu(\xx) = S[\ff](\xx) + D[\eeta](\xx),
\end{align}
where
\begin{align}
  S[\ff](\xx) &= \frac{1}{4\pi\mu} \int_{\gamma} \left(
    -\log \rho \mathds{I} + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) \, ds_\yy, \\
%
    D[\eeta](\xx) &= \frac{1}{\pi} \int_{\Gamma} 
      \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} \eeta(\yy) \, ds_\yy,
\end{align}
$\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times 2$
identity matrix. The corresponding pressure is
\begin{align}
  \label{eqn:pressure}
  p(\xx) = \frac{1}{2\pi} \int_{\gamma} \frac{\rr \cdot \ff}{\rho^2} \, ds_\yy + 
    \frac{1}{\pi} \int_{\Gamma} \frac{1}{\rho^2} 
    \left(\mathds{I} - 2\frac{\rr \otimes \rr}{\rho^2} \right) 
    \nn \cdot \eeta \, ds_\yy.
\end{align}

@@

We also report the excess pressure for the stenosis geometry and relate
it to the size of the lubrication layers. The excess pressure is the
additional pressure that is required to pass the vesicle through the
geometry when compared to the pressure necessary if the vesicle were
absent. Average pressures are calculated using
Equation~\eqref{eqn:pressure} along cross-sections that are parallel to
the flow direction near the inlet and outlet of the stenosis.
%, and the
%vesicle itself is never near these locations.

@@

When a vesicle is tank-treading near a solid wall, the flow in the thin
layer of fluid includes both a linear profile and a Poiseuille
profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
The magnitude of the Poiseuille profile is determined by the pressure
gradient between the vesicle and the solid wall, while the linear
profile is determined by the tangential velocity of the vesicle relative
to the solid wall. Using the definition of the lubrication layer
outlined in Section~\ref{sec:LL}, we consider the flow profile inside
this lubrication layer in Figure~\ref{fig:BLvelocities}. We observe that
the Poiseuille coefficient (quadratic term) can be either positive or
negative, meaning that the pressure gradient in the streamwise direction
in the lubrication layer switches signs. The Poiseuille coefficient is
related to the lateral gradient of the tangential traction,
$\mathbf{F}_\tt$, on the vesicle membrane~\cite{Oron1997_RMP,
Young2014_JFM}
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u}.
\end{align}
%is sufficiently large.
%to locally reverse the sign of the pressure
%gradient in the streamwise direction.
Here,
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the derivative of the membrane energy with respect to the lipid
concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential traction is $\mathbf{F}_\tt =
-\sigma_s$ which is the usual Marangoni effect.

@@

We conclude this example by considering the different shapes and
energies that single-component and multicomponent vesicles display.
Since we have initialized the lipid species to initially be phase
separated, the phase energy is nearly constant for all cases, and is
therefore not plotted. The tension energy, on the other hand, increases
as the vesicle approaches the neck, but its general shape is similar for
all five cases, and it too is not plotted. However, the bending energies
show different behaviors for each of the cases
(Figure~\ref{fig:bendingAll}).  The main difference being that the
multicomponent vesicles with a higher percentage of floppy regions have
less bending energy, especially as the vesicle passes through the neck.
We also note that the bending energy undergoes several transient
increases and decreases. These occur when the tail of the vesicle
undergoes transitions from lower energy shapes, such as `C' or `S'
shapes, to high energy shapes, such as `W' shapes.
Figure~\ref{fig:bendingSC_contracting} shows these different vesicle
shapes for the single-component vesicle and multicomponent vesicle that
is 45\% floppy. The shapes at several critical points along the bending
energy are included.
%and we can indeed see that transitioning vesicle shape between these
%different states.
